Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-06 inst/examples/20160715-slides-Krakow.Rmd
ok

# Set locale
Sys.setlocale(locale="UTF-8")

@@

# Selected time spam
df0 = bind_rows(fen, kun)
df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
```
---

@@

Idea: to study early modern knowledge production, all of it (1470-1830)

How? By combining library catalogue data (Fennica, Kungliga, ESTC, CERL)

What is important: to clean up the data (90% of the work) and to take into account how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.

How to fail: take worldcat or similar combination of datasets and analyse it as a whole without cleaning it first.

@@

### Data

Data used (1470-1828):

- Fennica, Finnish National Bibliography, 20328 documents

- Kungliga, National Library of Sweden's catalogue, 73165 documents

>>>>

# Set locale
tmp = Sys.setlocale(locale="UTF-8")

@@

# Selected time spam
df0 = bind_rows(fen, kun)
df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
```

@@

**Idea**: study early modern knowledge production, all of it (1470-1830)

**How?** By combining library catalogue data (Fennica, Kungliga, ESTC, CERL)

**Important**: to clean up the data (90% of the work) and to take into account how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.

**How to fail**: take worldcat or similar combination of datasets and analyse it as a whole without cleaning it first.

@@

### Data (1470-1828):

- Fennica (Finnish National Bibliography): 20328 documents

- Kungliga (National Library of Sweden): 73165 documents
